Type-Safe Modular Parsing

### 2017-01-08 paper/paper.tex
Revised abstract for submission

  This paper investigates solutions for the problem of \emph{modular
    parsing}. We focus on \emph{semantic} modularity and not just
  \emph{syntactic} modularity. That is, the solutions should not only
  allow complete parsers to be built out of modular parsing
  components, but also enable the parsing components to be
  \emph{modularly type-checked} and \emph{separately compiled}. We
  present \name: a parsing combinator library that enables modular
  parsing. Interestingly, the modularity requirements for modular
  parsing rule out several existing parsing combinator approaches,
  which rely on some non-modular techniques. We show that Packrat
  parsing techniques, provide solutions for such modularity problems,
  and enable reasonable performance in a modular setting.  Thus \name
  is built on top of a Packrat parsing library, but adds new parsing
  combinators to enable modular parsing. The new parsing combinators
  employ \emph{delegation-based} techniques and \emph{Object Algebras}
  to support extensibility. To evaluate \name we conduct a case study
  based on the ``Types and Programming Languages'' interpreters. The
  case study shows that \name is effective at reusing parsing code
  from existing interpreters, and the total parsing code is 60\%
  shorter than the non-modular parsing code.

>>>>

  This paper investigates solutions for the problem of \emph{modular
    parsing}. We focus on \emph{semantic} modularity and not just
  \emph{syntactic} modularity. That is, the solutions should not only
  allow complete parsers to be built out of modular parsing
  components, but also enable the parsing components to be
  \emph{modularly type-checked} and \emph{separately compiled}. We
  present a technique based parsing combinators that enables modular
  parsing. Interestingly, the modularity requirements for modular
  parsing rule out several existing parsing combinator approaches,
  which rely on some non-modular techniques. We show that Packrat
  parsing techniques, provide solutions for such modularity problems,
  and enable reasonable performance in a modular setting.
  Extensibility is achieved using \emph{Object Algebras}.  To evaluate
  the approach we conduct a case study based on the ``Types and
  Programming Languages'' interpreters. The case study the
  effectiveness at reusing parsing code from existing interpreters,
  and the total parsing code is 68\% shorter than the non-modular
  parsing code.
